KidsAIR: exposure model

### 2020-04-23 collinearity_exposure_analysis.Rmd
exposure analysis updates

Based on results and potential overlap, the following vars were removed:
         race_parent_2level, home_damp, moisture_closest_2level,
         temp_max_5, home_act_gas, total_residents_2level, home_type_2level, 
         home_windows_2level, home_fireplace, home_act_windows

@@

Initial variables to use for model selection (14):
Demographics: area, income_3level, residents_smoke
Home Characteristics: home_floors_2level, stove_age_3level,
                      chimney_clean_3level, home_mold, wood_collect_2level
Home Activity: home_act_door, home_act_smoking, home_act_sweep
Others: sums_events_sampling_period, mean_temp_sampling_period_5, stove_grade_3level

>>>>

Based on results and potential overlap, the following vars were removed:
         race_parent_2level, home_damp, 
         temp_max_5, home_act_gas, total_residents_2level, home_type_2level, 
         home_windows_2level, home_fireplace, home_act_windows

@@

Initial variables to use for model selection (14):
Demographics: area, income_3level, residents_smoke
Home Characteristics: home_floors_2level, stove_age_3level,
                      chimney_clean_3level, home_mold, wood_collect_2level
Home Activity: home_act_door, home_act_smoking, home_act_sweep
Others: sums_events_sampling_period, mean_temp_sampling_period_5, 
        stove_grade_3level, moisture_closest_2level,

### 2020-04-23 exposure_models.Rmd
exposure analysis updates

####### Format full data to use for analysis
analysis_data <- exposure_analysis_data_short %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  mutate(moisture_closest_2level = cut(moisture_closest, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE),
         moisture_winter_2level = cut(mean_moisture_winter, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE)) %>% 
  mutate(temp_max_2level = cut(temp_indoor_max, breaks = c(0, 30, 100),
                                 labels = c("<30", "30+"),
                                 right = FALSE),
         temp_min_2level = cut(temp_indoor_min, breaks = c(0, 16.5, 100),
                                 labels = c("<16.5", "16.5+"),
                                 right = FALSE),
         rh_max_2level = cut(rh_indoor_max, breaks = c(0, 40, 100),
                                 labels = c("<40", "40+"),
                                 right = FALSE),
         rh_min_2level = cut(rh_indoor_min, breaks = c(0, 20, 100),
                                 labels = c("<20", "20+"),
                                 right = FALSE)) %>% 
  mutate(sums_mean_sampling_period_5 = sums_mean_sampling_period/5,
         temp_perc_25_2level = cut(temp_perc_25, breaks = c(0, 50, 100),
                                 labels = c("<50", "50+"),
                                 right = FALSE),
         temp_perc_27_2level = cut(temp_perc_27, breaks = c(0, 35, 100),
                                 labels = c("<35", "35+"),
                                 right = FALSE),
         temp_perc_30_2level = cut(temp_perc_30, breaks = c(0, 10, 100),
                                 labels = c("<10", "10+"),
                                 right = FALSE)) %>% 
  left_join(sums_temp_change, by = c("area", "home")) %>% 
  left_join(ambient_data, by = c("area", "home")) %>% 
  select(-starts_with("home_act")) %>% 
  left_join(home_activity_data, by = c("area", "home")) %>% 
  select(pm_mean_sampling_period, area, income_3level,  
                 residents_smoke, home_floors_2level, stove_age_3level,  
                 chimney_clean_3level, home_mold, wood_collect_2level, 
                 home_act_door, home_act_smoking, home_act_sweep,
                 stove_grade_3level) %>% 
  filter(!is.na(pm_mean_sampling_period)) %>% 
  na.exclude()
```

Initial variables to use for model selection (14) from collinearity RMD:
Demographics: area, income_3level, residents_smoke
Home Characteristics: home_floors_2level, stove_age_3level,
                      chimney_clean_3level, home_mold, wood_collect_2level
Home Activity: home_act_door, home_act_smoking, home_act_sweep
Others: sums_events_sampling_period, mean_temp_sampling_period_5, stove_grade_3level

@@

```{r, include=FALSE}
full_model <- lm(log(pm_mean_sampling_period) ~ area + income_3level + 
                 residents_smoke + home_floors_2level + stove_age_3level + 
                 chimney_clean_3level + home_mold + wood_collect_2level +
                 home_act_door + home_act_smoking + home_act_sweep + 
                 stove_grade_3level,
                 data = analysis_data)

@@

all_subsets_aic <- dredge(full_model, rank = "AIC", extra = c("R^2"))
all_subsets_aicc <- dredge(full_model, rank = "AICc", extra = c("R^2"))
all_subsets_bic <- dredge(full_model, rank = "BIC", extra = c("R^2"))

@@

>>>>

####### Format full data to use for analysis
analysis_data <- exposure_analysis_data_short %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(area == "WMT") %>% 
  group_by(area, home) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  mutate(moisture_closest_2level = cut(moisture_closest, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE),
         moisture_winter_2level = cut(mean_moisture_winter, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE)) %>% 
  mutate(temp_max_2level = cut(temp_indoor_max, breaks = c(0, 30, 100),
                                 labels = c("<30", "30+"),
                                 right = FALSE),
         temp_min_2level = cut(temp_indoor_min, breaks = c(0, 16.5, 100),
                                 labels = c("<16.5", "16.5+"),
                                 right = FALSE),
         rh_max_2level = cut(rh_indoor_max, breaks = c(0, 40, 100),
                                 labels = c("<40", "40+"),
                                 right = FALSE),
         rh_min_2level = cut(rh_indoor_min, breaks = c(0, 20, 100),
                                 labels = c("<20", "20+"),
                                 right = FALSE)) %>% 
  mutate(sums_mean_sampling_period_5 = sums_mean_sampling_period/5,
         temp_perc_25_2level = cut(temp_perc_25, breaks = c(0, 50, 100),
                                 labels = c("<50", "50+"),
                                 right = FALSE),
         temp_perc_27_2level = cut(temp_perc_27, breaks = c(0, 35, 100),
                                 labels = c("<35", "35+"),
                                 right = FALSE),
         temp_perc_30_2level = cut(temp_perc_30, breaks = c(0, 10, 100),
                                 labels = c("<10", "10+"),
                                 right = FALSE)) %>% 
  left_join(sums_temp_change, by = c("area", "home")) %>% 
  left_join(ambient_data, by = c("area", "home")) %>% 
  select(-starts_with("home_act")) %>% 
  left_join(home_activity_data, by = c("area", "home")) %>% 
  select(pm_mean_sampling_period, area, income_3level, home_act_windows, 
                 stove_age_3level, home_windows_2level,
                 chimney_clean_3level, wood_collect_2level, 
                 home_act_door, home_act_smoking, home_act_sweep,
                 stove_grade_3level, moisture_closest_2level,
                 total_residents_2level, sums_events_sampling_period, mean_temp_sampling_period_5) %>% 
  filter(!is.na(pm_mean_sampling_period)) %>% 
  na.exclude()
```

Initial variables to use for model selection (14) from collinearity RMD:
Demographics: area, income_3level, residents_smoke
Home Characteristics: home_floors_2level, stove_age_3level,
                      chimney_clean_3level, home_mold, wood_collect_2level
Home Activity: home_act_door, home_act_smoking, home_act_sweep
Others: sums_events_sampling_period, mean_temp_sampling_period_5, 
        stove_grade_3level, moisture_closest_2level,

@@

Also try adding other variables in to check their impact on model selection:
   total_residents_2level (seems impactful), home_type_2level (not impactful), 
   home_windows_2level (seems impactful), home_act_windows (not very impactful),
   education_3level (not impactful)

Some vars not important in any models, so removing from consideration:
   home_mold, home_floors_2level, home_act_windows, home_type_2level

Next steps:
Some vars (like residents_smoke), other demographics, and home activity vars
have quite a bit of missing data. This is in addition to the missing ambient
and SUMs data. The first step should be to account for as much of this as possible.
See if there are ways to pull demographic data from Winter 2.
Then, see if data for WMT is more complete in general. The idea is to minimize
missing data for model selection and the final model to have as much power as
possible. 
Consider doing a more "full" model for WMT only (if there is less missing data),
particularly since the ambient data is more reliable for WMT than the other areas.
Then you could justify not doing a mixed model, and model selection would be easier.
Then, using data from all areas, use the full model from WMT to work on a 
mixed model that is likely reduced due to sparse data from the other areas.
Since model selection is difficult with mixed models, use the WMT model to inform
this model, while also doing sensitivity analysis to check other variables.
Aside from the multivariable model, much of the paper could also be looking at
simple associations between PM and some of the novel covars (SUMS, ambient data,
stove grades, wood moisture), as well as methods for collecting and analysing 
those vars.
Also look into predict() function for teach/test and validating the model.
Discussion can focus on what important predictors of indoor PM are in these homes - 
if simple demographic data predicts as well as complex things like SUMs and wood
moisture, or if there is a spectrum of predictors and complexity in their collection.

```{r, include=FALSE}
full_model <- lm(log(pm_mean_sampling_period) ~ income_3level + 
                 stove_age_3level + home_windows_2level +
                 chimney_clean_3level + wood_collect_2level + 
                 home_act_door + home_act_smoking + home_act_sweep + 
                 stove_grade_3level + moisture_closest_2level + 
                 total_residents_2level + mean_temp_sampling_period_5 +
                 sums_events_sampling_period, 
                 data = analysis_data)

@@

all_subsets_aic <- dredge(full_model, rank = "AIC", extra = c("R^2"))

all_subsets_aicc <- dredge(full_model, rank = "AICc", extra = c("R^2"))
par(mar = c(3,5,6,4))
plot(all_subsets_aicc)

all_subsets_bic <- dredge(full_model, rank = "BIC", extra = c("R^2"))

@@

#####################

Looking at Lasso and Ridge regression
May be beyond the scope of this paper, but keep code and references:

https://cran.r-project.org/web/packages/MuMIn/MuMIn.pdf

http://www.science.smith.edu/~jcrouser/SDS293/labs/lab10-r.html

https://cran.r-project.org/web/packages/glmnet/glmnet.pdf

https://cran.r-project.org/web/packages/glmmLasso/glmmLasso.pdf

https://arxiv.org/pdf/1306.2427.pdf

```{r} 
library(MuMIn)
library(leaps)
library(glmnet)
library(glmmLasso)

# Range of lambdas
grid = 10^seq(10, -2, length = 100)

lasso_results <- glmmLasso(log(pm_mean_sampling_period) ~ income_3level + 
                 residents_smoke + stove_age_3level + home_windows_2level +
                 chimney_clean_3level + wood_collect_2level + 
                 home_act_door + home_act_smoking + home_act_sweep + 
                 stove_grade_3level + moisture_closest_2level + 
                 total_residents_2level,
                 rnd = list(area = ~ 1), 
                 lambda = grid,
                 data = analysis_data)

summary(lasso_results)

predict(lasso_results)
```
